Object-based Auditory Scenes Similarity Retrieval and Classification With Wavelet Scattering

### 2016-07-11 paper/structureScene.tex
clean ml comments

\ml{gregoire: une figure avec un clustering et une annotation ?}

@@

\ml{detail: put in experimental part using an enhanced version of the popular K-means algorithm known as $K$-means$++$ \cite{arthur2007k}, which differs from k-means method in terms of selection of starting points. }

@@

\ml{Grégoire : if the matrix is not psd, then this is NOT a kernel, reformulate}

@@

For the ASC setting, the systems are evaluated  with five-fold  stratified cross validation on the private dataset of the DCASE 2013 challenge. The folds are identical to those used in the original challenge. Optimal parameters (see above) are this time learned on the public dataset of the DCASE 2013 challenge, using five-fold  stratified cross validation as well.

>>>>

@@

@@

%\ml{Grégoire : if the matrix is not psd, then this is NOT a kernel, reformulate}

@@

For the ASC setting, the systems are evaluated  with five-fold  stratified cross validation on the private dataset of the DCASE 2013 challenge. The folds are identical to those used in the original challenge. Optimal parameters (see above) are this time learned on the public dataset of the DCASE 2013 challenge, using five-fold  stratified cross validation as well. Clustering is done using an enhanced version of the popular K-means algorithm known as $K$-means$++$ \cite{arthur2007k}, which differs from k-means method in terms of selection of starting points.
